Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-06-01 paper/AlignedIsotropicGW.tex
Close #41; more specific about models that give 1.7sigma.
Close #42, moving paragraph on dynamical formation out from between isolated formation 'graphs.
Close #43, make clear 'isolated binary black holes' not just 'binaries'.

\begin{figure}
  \plotone{../plots/Wills_evidence_ratio_figure_with_mixture_models}
  \caption{\textbf{Odds ratios among our models using the
      approximations to the posteriors on $\chieff$ from the O1
      observations shown in Figure \ref{fig:O1-posteriors}.}  The flat
    (``F''), high (``H''), and low (``L'') spin magnitude
    distributions (see Eq.\ \eqref{eq:magnitude-dists}) are paired
    with isotropic (``I'') and aligned (``A'') angular distributions,
    as well as a mixture model of the two (``$\mathrm{M}$'').  The
    most-favoured models have the ``low'' distribution of spin
    magnitudes.  The odds ratio between these models is
    $\OOneOddsIsoAligned$, or $\OOneSigmaIsoAligned\sigma$.  For all
    magnitude distributions the pure-isotropic models are preferred
    over the mixture models; correspondingly, the posterior on the
    mixture fraction peaks at 100\% isotropic.}
  \label{fig:O1-odds}
\end{figure}

@@

@@

The spin directions in isolated
binaries\cite{TutukovYungelson:1973,TutukovYungelson:1993,Lipunov:1997,2016Natur.534..512B,Stevenson:2017,MandeldeMink:2016,Marchant:2016}
are usually expected to be preferentially aligned.  Despite observed
spin-orbit misalignments in both massive stellar
binaries\cite{Albrecht:2009,2014ApJ...785...83A} and BH X-ray
binaries\cite{Orosz:2001,Martin:2008b,Martin:2008,MorningstarMiller:2014},
mass accretion and tidal interactions will tend to realign the binary.
On the other hand, a supernova natal kick (if any) can change the
orbital plane and misalign the
binary\cite{2000ApJ...541..319K,2013PhRvD..87j4028G}; the supernova
can also tilt the spin angle, as in the double pulsar
J0737-3039\cite{2011ApJ...742...81F}.  Evolutionary processes, such as
wind-driven mass loss and post-collapse fallback, can couple the spin
magnitude and direction distributions, contrary to our simplified
assumptions.  A small misalignment at wide separation can also evolve
to a more significant misalignment in component spins as the binary
spirals in through \ac{GW} emission\cite{2015PhRvD..92f4016G}, but
$\chieff$ is approximately conserved through this evolution.

>>>>

\begin{figure}
  \plotone{../plots/Wills_evidence_ratio_figure_with_mixture_models}
  \caption{\textbf{Odds ratios among our models using the
      approximations to the posteriors on $\chieff$ from the O1
      observations shown in Figure \ref{fig:O1-posteriors}.}  The flat
    (``F''), high (``H''), and low (``L'') spin magnitude
    distributions (see Eq.\ \eqref{eq:magnitude-dists}) are paired
    with isotropic (``I'') and aligned (``A'') angular distributions,
    as well as a mixture model of the two (``$\mathrm{M}$'').  The
    most-favoured models have the ``low'' distribution of spin
    magnitudes.  The odds ratio between the best aligned and best
    isotropic models is $\OOneOddsIsoAligned$, or
    $\OOneSigmaIsoAligned\sigma$.  For all magnitude distributions the
    pure-isotropic models are preferred over the mixture models;
    correspondingly, the posterior on the mixture fraction peaks at
    100\% isotropic.}
  \label{fig:O1-odds}
\end{figure}

@@

The spin directions in isolated binary black
holes\cite{TutukovYungelson:1973,TutukovYungelson:1993,Lipunov:1997,2016Natur.534..512B,Stevenson:2017,MandeldeMink:2016,Marchant:2016}
are usually expected to be preferentially aligned.  Despite observed
spin-orbit misalignments in both massive stellar
binaries\cite{Albrecht:2009,2014ApJ...785...83A} and BH X-ray
binaries\cite{Orosz:2001,Martin:2008b,Martin:2008,MorningstarMiller:2014},
mass accretion and tidal interactions will tend to realign the binary.
On the other hand, a supernova natal kick (if any) can change the
orbital plane and misalign the
binary\cite{2000ApJ...541..319K,2013PhRvD..87j4028G}; the supernova
can also tilt the spin angle, as in the double pulsar
J0737-3039\cite{2011ApJ...742...81F}.  Evolutionary processes, such as
wind-driven mass loss and post-collapse fallback, can couple the spin
magnitude and direction distributions, contrary to our simplified
assumptions.  A small misalignment at wide separation can also evolve
to a more significant misalignment in component spins as the binary
spirals in through \ac{GW} emission\cite{2015PhRvD..92f4016G}, but
$\chieff$ is approximately conserved through this evolution.

@@
